Notes for ISIPTA poster

### 2016-06-24 asce-paper.tex
suggestion Frank for elicitation part
working on intro

@@

***reuse ESREL paper intro

@@

>>>>

***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''

@@

In reliability engineering, a central task is to describe the reliability of a complex system.
This is usually done by determining the \emph{reliability function} $R(t)$,
in other contexts also known as the \emph{survival function} $S(t)$,
giving the probability that the system has not failed by time $t$:
\begin{align}
R_\text{sys}(t) = P(T_\text{sys} \geq t)\,,
\end{align}
where $T_\text{sys}$ is the random variable giving the failure time of the system. %
%\footnote{}
Based on the distribution of $T_\text{sys}$, which can also be expressed
in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - R_\text{sys}(t)$,
the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
decisions about, e.g., scheduling of maintenance work can be made.

Often, there is no failure data for the system itself
(e.g., if the system is a prototype, or the system is used under unique circumstances),
but there is some information about failure times for the components the system is made of.
Information on the distribution of component failure times $T_i$,
where $i = 1, \ldots, n$ if the system consists of $n$ components,
can then be used to derive the distribution of $T_\text{sys}$.
In this paper, we consider*** a simple parallel system
where all components are of the same type,
and our observations consist solely of the failure times of one or more components in this system.
%In the last section, we will briefly describe
%how the approach can be generalized to arbitrary system structures
%using the survival signature \cite{2012:survsign},
%which allows for different types of components and
%the inclusion of data from component tests, as in \citeNP{2014:bayessurvsign}.
%
We assume a parametric probability distribution for component lifetimes $T_i$. 
The Bayesian approach allows to base estimation of the component failure distributions
on both data and further knowledge not given by the data,
the latter usually provided in the form of expert knowledge.
This knowledge is encoded in form of a so-called prior distribution,
a distribution on the parameter(s) of the component lifetime distribution.
This expert knowledge is especially important when there is very few data on the components (like in our scenario),
as only with its help meaningful estimates for the system reliability can be made.

@@

\section{elicitation}

*** prior via pseudo-observations, can contain censored pseudo-data

*** cf paper from Frank 20ys ago (?)
